%%%% Time-stamp: <2013-02-25 10:31:01 vk>

\begin{thebibliography}{9}
  \bibitem{master_nuno}
  N. Passos.
  \textit{Poker Learner: Reinforcement Learning Applied to Texas Hold'em Poker},
  Master's thesis, Faculdade de Engenharia da Universidade do Porto, Portugal, 
  2011.
  \href{https://paginas.fe.up.pt/$\sim$ei08029/Master\%20Thesis\%20-\%20Nuno\%20Passos.pdf}{\markblue{https://paginas.fe.up.pt/$\sim$ei08029/Master Thesis - Nuno Passos.pdf}}
  \bibitem{strong_poker}
   J. Schaeffer, D. Billings, L. Pe$\tilde{n}$a, and D. Szafron.
  \textit{Learning to Play Strong Poker}.
  ICML-99, Proceedings of the 16th International Conference on Machine Learning, 
  1999.
  \href{http://poker.cs.ualberta.ca/publications/ICML99.pdf}{\markblue{http://poker.cs.ualberta.ca/publications/ICML99.pdf}}
  \bibitem{pena}
  L. Pe$\tilde{n}$a.
  \textit{Probabilities and simulations in poker.}
  Mather's thesis, Department of Computing Science, University of Alberta,
  1999.
\bibitem{review}
  J. Rubin, and I. Watson.
  \textit{Computer poker: A review.}
   Artificial Intelligence, 175(5-6):958-987,
  2011.
\bibitem{theory_of_poker}
  D. Sklansky.
  \textit{The Theory of Poker.}
   Two Plus Two Publishing,
  2005.
\bibitem{billings_phd}
  D. Billings.
  \textit{Algorithms and Assessment in Computer Poker}
   Ph.D. Dissertation, University of Alberta,
  2006.
\bibitem{poker_dummies}
  R. D. Harroch, and L. Krieger.
  \textit{Poker For Dummies.}
   John Wiley \& Sons, 1st Edition,
  2000.
\bibitem{game_theory}
  M. J. Osborne.
  \textit{A Course in Game Theory.}
   The MIT Press, Cambridge, Massachusetts, London, England,
  2014.
\bibitem{quality_of_bots}
  V. Lisy, and M. Bowling.
  \textit{Equilibrium Approximation Quality of Current No-Limit Poker Bots.}
   arXiv preprint arXiv:1612.07547,
  2017.
\bibitem{selective_sampling}
  D. Billings, L. Pe$\tilde{n}$e, J. Schaeffer, D. Szafron.
  \textit{Using Probabilistic Knowledge and Simulation to Play Poker.}
   In 16th National Conference on Artificial
Intelligence, pp. 697-703,
  1999.
\bibitem{opp_modeling}
  D. Billings, D. Papp, J. Schaeffer, and D. Szafron.
  \textit{Opponent Modeling in Poker.}
   Proc. AAAI-98, Madison, WI, pp. 493-499,
  1998.
\bibitem{opp_master}
  A. Davidson.
  \textit{Opponent modeling in poker: Learning and acting in a hostile and uncertain environment.}
   Master’s thesis, University of Alberta, 
  2002.
\bibitem{ENN_garrett}
G. Nicolai, and R. J. Hilderman.
\textit{No-Limit Texas Hold'em Poker Agents Created with Evolutionary Neural Networks.}
CIG-2009, IEEE Symposium on Computational Intelligence and Games, pp. 125-131, 2009.
\bibitem{evolutionary_methods}
G. Nicolai.
\textit{Evolutionary methods for learning no-limit Texas hold'em poker.} Master's thesis, University of Regina, 2008.
\bibitem{challenge_of_poker}
D. Billings, A. Davidson, J. Schaeffer, and D. Szafron.
\textit{The Challenge of Poker}
Artificial Intelligence 134, pp. 201?240, 2002.
\bibitem{hand_eval}
L. F. Teofilo.
\textit{Estimating the Probability of Winning for Texas Hold'em Poker Agents}.
Proceedings 6th Doctoral Symposium on Informatics Engineering, pp 129-140. Porto, Portugal.
\end{thebibliography}


%\glsresetall %% all glossary entries should be used in long form (again)
%% vim:foldmethod=expr
%% vim:fde=getline(v\:lnum)=~'^%%%%\ .\\+'?'>1'\:'='
%%% Local Variables:
%%% mode: latex
%%% mode: auto-fill
%%% mode: flyspell
%%% eval: (ispell-change-dictionary "en_US")
%%% TeX-master: "main"
%%% End:
